---
title: "pptfig overview and examples"
author: "Eben Pendleton"
date: "2021-02-15"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{pptfig overview and examples}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Introduction
Welcome to an overview and examples for Integral's PowerPoint theme, __ppttheme()__
and figure function, __pptfig()__.
The first step is to load the library.
```{r setup}
# load the library
library(integral)
```
The library has two functions, ppttheme() which is a theme associated with 
ggplot2 and pptfig() which handles placing the figures in
the PowerPoint template. 

## ppttheme()
The current ppttheme() is shown below. 
```{r}
#' theme for PowerPoint slide
ppttheme <- function() {
  return(ggplot2::theme(text = ggplot2::element_text(family = "sans")) +
    ggplot2::theme_bw() +
    ggplot2::theme(
      legend.title = ggplot2::element_blank(), legend.text = ggplot2::element_text(color = "black", size = 8),
      legend.background = ggplot2::element_rect(size = .5, linetype = "solid", color = "black")
    ) +
    ggplot2::theme(
      panel.grid.minor = ggplot2::element_blank(),
      panel.background = ggplot2::element_blank(),
      axis.line = ggplot2::element_line(colour = "black", size = 1)
    ) +
    ggplot2::theme(axis.text.x = ggplot2::element_text(color = "black", size = 8, vjust = 0.5, angle = 0)) +
    ggplot2::theme(axis.text.y = ggplot2::element_text(color = "black", size = 8, vjust = 0.5, angle = 0)) +
    ggplot2::theme(axis.title.x = ggplot2::element_text(color = "black", size = 9, face = "bold")) +
    ggplot2::theme(axis.title.y = ggplot2::element_text(color = "black", size = 9, face = "bold")) +
    ggplot2::theme(plot.title = ggplot2::element_text(size = 10, hjust = 0.5, face = "bold")) +
    ggplot2::theme(axis.ticks = ggplot2::element_line(size = 1)) +
    ggplot2::theme(axis.line = ggplot2::element_line(size = 1)) +
    ggplot2::theme(strip.background = ggplot2::element_rect(fill = "white")) +
    ggplot2::theme(panel.border = ggplot2::element_rect(fill = NA, size = 0.25)) +
    ggplot2::theme(strip.text = ggplot2::element_text(face = "bold", size = 9)) +
    ggplot2::theme(plot.margin = ggplot2::unit(c(0.5, 0.5, .5, 0.5), "cm")))
}
```

This theme is loaded from the library in the example below
```{r}
theme <- integral::ppttheme()
```

## pptfig()
pptfig() handles placing the figures in
the PowerPoint template. 

An example using letter and landscape is below. 
```{r}
# used to read data for this example
library(dataRetrieval)
# library in this vignette
library(integral)
# library for graphics creation
library(ggplot2)
# library to convert graphics to Office compatible graphic
library(rvg)

###Theme
theme <- integral::ppttheme()
###Data
Q <- dataRetrieval::readNWISuv(site = "01114500", parameterCd = "00060", startDate = as.Date("2020-01-01"))

###Figure
p <- ggplot() +
  geom_path(data = Q, aes(x = dateTime, y = X_00060_00000)) +
  geom_hline(yintercept = 200, color = "red", size = 1.5) +
  annotate("text", x = as.POSIXct("2020-04-01"), y = 200, label = "Line", vjust = 1.8) +
  labs(title = "USGS Stream Gage 01114500, 2020", x = NULL, y = "Discharge (cfs)") +
  theme

###pptfig
### landscape 11 x 8.5
orientation <- "L"
size <- "letter"
fig <- rvg::dml(ggobj = p)
section <- "X"
fig.num <- 1
doc.title.1 <- "Discharge at USGS Stream Gage 01114500"
doc.title.2 <- "Project Description 1"
doc.title.3 <- "Project Description 2"
draft <- "DRAFT"
note <- "Note: Data pulled using readNWISuv."
author <- "Eben Pendleton"

my_pres <- read_pptx_template(size, orientation)

my_pres <- pptfig(my_pres, size, orientation, fig, section, fig.num, note, author, doc.title.1,
                  doc.title.2, doc.title.3, draft)

print(my_pres, "OutputL11x8.5.pptx")
```


An example using letter and legal presentations sizes is below.
```{r}
# used to read data for this example
library(dataRetrieval)
# library in this vignette
library(integral)
# library for graphics creation
library(ggplot2)
# library to convert graphics to Office compatible graphic
library(rvg)

###Theme
theme <- integral::ppttheme()
###Data
Q <- dataRetrieval::readNWISuv(site = "01114500", parameterCd = "00060", startDate = as.Date("2020-01-01"))

###Figure
p <- ggplot() +
  geom_path(data = Q, aes(x = dateTime, y = X_00060_00000)) +
  geom_hline(yintercept = 200, color = "red", size = 1.5) +
  annotate("text", x = as.POSIXct("2020-04-01"), y = 200, label = "Line", vjust = 1.8) +
  labs(title = "USGS Stream Gage 01114500, 2020", x = NULL, y = "Discharge (cfs)") +
  theme

###pptfig
### landscape 11 x 8.5
orientation <- "L"
size <- "letter"
fig <- rvg::dml(ggobj = p)
section <- "X"
fig.num <- 1
doc.title.1 <- "Discharge at USGS Stream Gage 01114500"
doc.title.2 <- "Project Description 1"
doc.title.3 <- "Project Description 2"
draft <- "DRAFT"
note <- "Note: Data pulled using readNWISuv."
author <- "Eben Pendleton"
my_pres <- read_pptx_template(size, orientation)

my_pres <- pptfig(my_pres, size, orientation, fig, section, fig.num, note, author, doc.title.1,
                  doc.title.2, doc.title.3, draft)

print(my_pres, "OutputL11x8.5.pptx")

### portrait 8.5 x 11
size <- "letter"
orientation <- "P"
fig <- rvg::dml(ggobj = p)
section <- "X"
fig.num <- 1
doc.title.1 <- "Discharge at USGS Stream Gage 01114500"
doc.title.2 <- "Project Description 1"
doc.title.3 <- "Project Description 2"
draft <- "DRAFT"
note <- "Note: Data pulled using readNWISuv."
author <- "Eben Pendleton"

my_pres <- read_pptx_template(size, orientation)

my_pres <- pptfig(my_pres, size, orientation, fig, section, fig.num, note, author, doc.title.1,
                  doc.title.2, doc.title.3, draft)
print(my_pres, "OutputP8.5x11.pptx")

# ledger
# landscape 17 x 11
size <- "ledger"
orientation <- "L"
fig <- rvg::dml(ggobj = p)
section <- "X"
fig.num <- 1
doc.title.1 <- "Discharge at USGS Stream Gage 01114500"
doc.title.2 <- "Project Description 1"
doc.title.3 <- "Project Description 2"
draft <- "DRAFT"
note <- "Note: Data pulled using readNWISuv."
author <- "Eben Pendleton"

my_pres <- read_pptx_template(size, orientation)

my_pres <- pptfig(my_pres, size, orientation, fig, section, fig.num, note, author, doc.title.1,
                  doc.title.2, doc.title.3, draft)

print(my_pres, "OutputL17x11.pptx")
#
# ### portrait 11 x 17
size <- "ledger"
orientation <- "P"
fig <- rvg::dml(ggobj = p)
section <- "X"
fig.num <- 1
doc.title.1 <- "Discharge at USGS Stream Gage 01114500"
doc.title.2 <- "Project Description 1"
doc.title.3 <- "Project Description 2"
draft <- "DRAFT"
note <- "Note: Data pulled using readNWISuv."
author

my_pres <- read_pptx_template(size, orientation)
my_pres <- pptfig(my_pres, size, orientation, fig, section, fig.num, note, author, doc.title.1,
                  doc.title.2, doc.title.3, draft)
print(my_pres, "OutputP11x17.pptx")
```



